Dark matter halo concentrations with a bayesian approach

### 2014-05-26 paper/article.tex
update on the data

We select a sample of halos in a cubic sub-volumne of $XXX$ \hMpc on a
side. We select first all the halos at $z=0$ detected with a
Friends-of-Friends (FoF) algorithm with masses in the interval $10^{11}\leq
M_{\rm FoF}/\hMsun \leq 10^{15}$. The FoF algorithm ran with a linking
length of $0.17$ times the average interparticle distance. This choice
translates into an overdensity $\Delta_h\sim 700$ that is dependent on
the halo concentration \citep{More2011}.

>>>>

We select a sample of halos in a cubic sub-volumne of $100$ \hMpc on a
side centered on the most massive halo in the simulation at
$z=0$\footnote{This corresponds to the \texttt{miniMDR1} database in
  the MultiDark webpage}. We select first all the halos at $z=0$
detected with a Friends-of-Friends (FoF) algorithm with masses in the
interval $10^{11}\leq M_{\rm FoF}/\hMsun \leq 10^{15}$. The FoF
algorithm ran with a linking length of $0.17$ times the average
interparticle distance. This choice translates into an overdensity
$\Delta_h\sim 700$ that is dependent on the halo concentration
\citep{More2011}.
